### 2023-12-14 manuscript.tex
Autocommit

There were three models in this study.  The main one is the “daughter” model, which analyzed associations of beliefs of FGC benefits (see the list of FGC benefits at table xx) and behavioral intention to have their daughters receiving FGC.  Additionally, we decomposed the model into two “structural” models:  structural one “continuance” model to study women’s beliefs of FGC benefits and FGC continuance; and structural two “persistence”  model \cf{or “mixed” model?} to examine the association of beliefs of FGC benefits, FGC continuence and intention of genitally cutting daughters.  We used the two structural models to further understand how such positions change the main model.

@@

We conducted secondary analysis of women aged 15-49 in the Demographic and Health Surveys (DHS) with FGC benefit and gender awareness modules in countries with high FGC prevalence \cite{UNIC16}. Four countries qualified under this criteria with the most recent complete data set from each: Kenya 2008/9, Mali 2006, Nigeria 2008 and Sierra Leone 2008.  \cfcmt{checked and updated in Nov 6, 2023.   The datasets are pretty old but were the most recent ones with FGC benefits modules.  See FGC main page for updated info.}.  Since one of our main research interests was to detect relationship of normative attitudes and intentional behaviors of circumcising daughters, the findings should not be compromised due to the time of the data collected.

>>>>

There were three models in this study:  the daughter model, the continuance model and the persistence model.  The main one is the “daughter” model, which analyzed associations of beliefs of FGC benefits (see the list of FGC benefits at table xx) and behavioral intention to have their daughters receiving FGC.  Additionally, we decomposed the model into two “structural” models:  structural one “continuance” model to study women’s beliefs of FGC benefits and FGC continuance; and structural two “persistence”  model \cf{or “mixed” model?} to examine the association of beliefs of FGC benefits, FGC continuance and intention of genitally cutting daughters.  We used the two structural models to further understand how such positions change the main model.

@@

We analyzed the secondary data of women aged 15-49 in the Demographic and Health Surveys (DHS).  The DHS was selected when it met the study criteria:  countries with high FGC prevalence \cite{UNIC16} with the modules of FGC benefit and gender awareness. Four countries qualified under this criteria with the most recent complete data set from each: Kenya 2008/9, Mali 2006, Nigeria 2008 and Sierra Leone 2008.  \cfcmt{checked and updated in Nov 6, 2023.   The datasets are pretty old but were the most recent ones with FGC benefits modules.  See FGC main page for updated info.}.  Since one of our main research interests was to detect relationship of normative attitudes and intentional behaviors of circumcising daughters, the findings should not be compromised due to the time of the data collected.
